SDR enhancement by clouds

### 2024-03-20 article/article.Rmd
Commit 2024-03-20 10:14
Commit 2024-03-20 11:12

We computed the daily trend of the mean over irradiance of CE (Figure\ 
\ref{fig:CEmeanDaily}), using a first-order autoregressive model with lag of 1 day,
using the 'maximum likelihood' fitting method [@Gardner1980; @Jones1980] by
implementing the function 'arima' from the library 'stats' of the R programming
language [@RCT2023]. The trends were reported together with the $2\sigma$ error.
We observe an increase of
$`r round(dailyCE[var == "GLB_diff.mean", Tmod_Estimate], 3)`\pm
`r round(2 * dailyCE[var == "GLB_diff.mean", Tmod_Std..Error], 3)`\,W/m^2$
on the mean over irradiance.

@@

Although, the previous result is closer to the raw data, we preferred to present the
annual statistics, that give a more clear picture about the long term CE trends.
Hence, we calculated the annual values from the one-minute measurements.
The annual mean over irradiance is
$`r round(yearlyCE[var == "GLB_diff.mean", slope], 2)`\pm
`r round(2 * yearlyCE[var == "GLB_diff.mean", slope.sd], 2)`\,W/m^2$
(Figure\ \ref{fig:P-energy-mean}),
but this value is not very useful due the high
variability of this metric.

@@

A better indicator of changes on the characteristic of CE would be the number of CE
occurrences and the total energy of the CE over irradiance. The annual number of CE
occurrences, shows a steady increase of
$`r round(yearlyCE[var == "GLB_diff.N", slope], 1)`\pm
`r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,/y$
(Figure\ \ref{fig:P-energy-N}).

@@

Another interesting aspect of the CE cases, is the seasonal cycle. In Figure\ 
\ref{fig:relative-month-occurancies}, we have the box plot (whisker plot), where the
values have been normalized by the highest median value, that occurs in May.
Although the number of occurrences has a wide spread throughout the study period,
the most active period of CE occurrences is during May and June. During the Winter
(December -- February) the CE cases are about 25% of the maximum. The rest of the
months the occurrences seems to ramp between the maximum and minimum.

@@

```{r echo=FALSE, fig.cap="Distribution of CE over irradiance"}
knitr::include_graphics("../images/P-relative-distribution-diff-1.png")
```

@@

```{r echo=FALSE, fig.cap="Distribution of CE groups"}
knitr::include_graphics("../images/groups-1.png")
```

```{r echo=FALSE, fig.cap="Relation of mean over irradiance and CE group duration"}
knitr::include_graphics("../images/groups-4.png")
```

```{r echo=FALSE, fig.cap="Relation of maximun over irradiance and CE group duration"}
knitr::include_graphics("../images/groups-8.png")
```

@@

```{r echo=FALSE, fig.cap="Distribution of ECE Irradiance above 'TSI'"}
knitr::include_graphics("../images/extremedistributions-4.png")
```

>>>>

We computed the daily trend of the mean over irradiance of CE
(Figure\nobreakspace{}\ref{fig:CEmeanDaily}), using a first-order autoregressive
model with lag of 1 day, using the 'maximum likelihood' fitting method [@Gardner1980;
@Jones1980] by implementing the function 'arima' from the library 'stats' of the R
programming language [@RCT2023]. The trends were reported together with the $2\sigma$
error.  We observe an increase of
$`r round(dailyCE[var == "GLB_diff.mean", Tmod_Estimate], 3)`\pm
`r round(2 * dailyCE[var == "GLB_diff.mean", Tmod_Std..Error], 3)`\,W/m^2$
on the mean over irradiance.

@@

Although, the previous result is closer to the raw data, we preferred to present the
annual statistics, that give a more clear picture about the long term CE trends.
Hence, we calculated the annual values from the one-minute measurements.
The annual mean over irradiance is
$`r round(yearlyCE[var == "GLB_diff.mean", slope], 2)`\pm
`r round(2 * yearlyCE[var == "GLB_diff.mean", slope.sd], 2)`\,W/m^2$
(Figure\nobreakspace{}\ref{fig:P-energy-mean}),
but this value is not very useful due the high
variability of this metric.

@@

A better indicator of changes on the characteristic of CE would be the number of CE
occurrences and the total energy of the CE over irradiance. The annual number of CE
occurrences, shows a steady increase of
$`r round(yearlyCE[var == "GLB_diff.N", slope], 1)`\pm
`r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,/y$
(Figure\nobreakspace{}\ref{fig:P-energy-N}).
We have to note that the energy related to the CE events can not be directly linked
with the total energy balance on the atmosphere. The net sun radiation of the region
is not increased, but rather redistributed through the CE.

@@

Another interesting aspect of the CE cases, is the seasonal cycle. In
Figure\nobreakspace{}\ref{fig:relative-month-occurancies}, we have the box plot
(whisker plot), where the values have been normalized by the highest median value,
that occurs in May.  Although the number of occurrences has a wide spread throughout
the study period, the most active period of CE occurrences is during May and June.
During the Winter (December -- February) the CE cases are about 25% of the maximum.
The rest of the months the occurrences seems to ramp between the maximum and minimum.

@@

The distribution of the CE over irradiance spreads uniformly
Figure\nobreakspace{}\ref{fig:ovir-distribution}. Where there is an inverse relation
between the events frequency and events intensity. This is expected as, the stronger
the CE events become, the more rare are the particular atmospheric and sun conditions
to occur.

```{r ovir-distribution, echo=FALSE, fig.cap="Distribution of CE over irradiance"}
knitr::include_graphics("../images/P-relative-distribution-diff-1.png")
```

@@

In order to further study the characteristics of the CE events, we grouped the singe
minute CE events, to continuous CE groups (CEG). Thus, a CEG consists of one or more
successive CE cases, and can have a duration of multiple of minutes.  We have
identified `r ST_G0[, .N]` groups, where the group with the longest duration lasted
`r ST_G0[, max(GLB_diff.N)]` minutes on 
`r strftime(ST_G0[which.max(GLB_diff.N), Date], "%d\\ %B %Y")`.
By examining the frequency distribution of the CEG durations
(Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}), is evident that durations above
10 minutes are very rare.

```{r ceg-duration-distribution, echo=FALSE, fig.cap="Distribution of CE groups"}
knitr::include_graphics("../images/groups-1.png")
```

... @Zhang2018 ....

```{r echo=FALSE, fig.cap="Relation of mean over irradiance and CE group duration"}
knitr::include_graphics("../images/P-groups-bin2d-1.png")
```

<!-- ```{r echo=FALSE, fig.cap="Relation of mean over irradiance and CE group duration"} -->
<!-- knitr::include_graphics("../images/groups-4.png") -->
<!-- ``` -->

<!-- ```{r echo=FALSE, fig.cap="Relation of maximun over irradiance and CE group duration"} -->
<!-- knitr::include_graphics("../images/groups-8.png") -->
<!-- ``` -->

@@

<!-- ```{r echo=FALSE, fig.cap="Distribution of ECE Irradiance above 'TSI'"} -->
<!-- knitr::include_graphics("../images/extremedistributions-4.png") -->
<!-- ``` -->
